---
title: "Lab 10"
author: "Adam Orr"
date: "November 3, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
section: 91973 Friday 9am
code: lab10.R
---



```{r setup, include=FALSE}
knitr::read_chunk(rmarkdown::metadata$code)
```

Section: `r rmarkdown::metadata$section`

## Question 1
###Script
```{r question 1, eval = FALSE, fig.width=7, fig.height=7}
```

###Output
```{r question 1, echo = 7, fig.width=7, fig.height=7}
```

###Answers

## Question 2
###Script
```{r question 2, eval = FALSE}
```
###Output
```{r question 2, echo = c(1,2)}
```

###Answers
*Use your results to fill in an ANOVA table like the one below.*

 Category | df | SS | MS | F | P 
 --- | --- | --- | --- | --- | --- 
 Treatment | `r df_treatment` | `r SS_treatment` | `r MS_treatment` | `r fval` | 5.18e-5 | x
 Error | `r df_error` | `r SS_error` | `r MS_error` | |  

*In addition, make a clear statement of the null and alternative hypotheses that you tested and the results of your test.*

H<sub>0</sub>: The mean of each treatment group is the same.

H<sub>a</sub>: There is a mean group that is not the same as the others.

With a confidence level of 0.05, I reject the null hypothesis that the mean of each treatment group is identical (ANOVA, F<sub>`r df_treatment`,`r df_error`</sub> = `r round(fval,3)`, p = 5.18e-5).

## Question 3
###Script
```{r question 3, eval = FALSE}
```
###Output
```{r question 3, echo = 1}
```

###Answers

## Question 4
###Script
```{r question 4, eval = FALSE}
```
###Output
```{r question 4, echo = c(1,4)}
```

###Answers

## Question 5
###Script
```{r question 5, eval = FALSE}
```
###Output
```{r question 5, echo = c(1,4)}
```

###Answers
*Do these tests by hand and present your results in a table like this:*
```{r echo = FALSE, results = 'asis'}
library(knitr)
kable(tukeytable)
```

## Question 6
###Script
```{r question 6, eval = FALSE}
```
###Output
```{r question 6, echo = 1}
```

###Answers

## Question 7
###Script
```{r question 7, eval = FALSE}
```
###Output
```{r question 7, echo = c(1:3), fig.width=7, fig.height=7}
```

###Answers
