---
title: "Mass Spectrometry Biomarker Discovery"
author: "Adam Orr"
date: "November 26, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
section: 91973 Friday 9am
code: term_project.R
---

```{r setup, include=FALSE}
knitr::read_chunk(rmarkdown::metadata$code)
```

Section: `r rmarkdown::metadata$section`

#Introduction

Mass spectrometry is the process of ionizing a sample and sorting its component molecules by mass to charge ratio.
It is often used to identify the compounds that make up an unknown mixture.
Some compounds found in human samples may be identifiable in mass spectrometry data, and may be significant indicators of health status.
In this case, we are interested in developing a diagnostic test to determine if mass spectrometry analysis of human urine can determine whether a person is infected with Valley Fever, a fungal infection of the lungs.

We hypothesize that peaks found in mass spectrometry analysis of human urine are significantly associated with health status. Additionally, we hypothesize that increasing the number of these peaks detected in a sample significantly increases the probability that the donating individual is diseased.

#Methods

We have collected urine samples from 10 individuals affected with Valley Fever, and urine samples from 10 random, non-affected individuals. We then subjected these to a mass spectrometer, yielding a mass to charge ratio for each ion detected in each of the 20 samples.

We then created a contingency table for each peak detected, with the health status of the donor as one variable and whether the peak was present or absent as the other. These contingency tables were then used to perform a Fisher's Exact Test on each peak to test whether the presence of the peak is significantly associated with health status.
P-values were then corrected for multiple comparisons by Holm's correction. The peaks that had corrected p-values less than 0.05 were collected.
All corrected p-values were then plotted.

We were interested in whether an increase in the number of significant peaks detected in a sample increased the probability that the individual is infected.
We therefore performed a logistic regression on the number of significant peaks in each sample and whether the donor was infected or not.
Though logistic regression does not assume that residuals are normally or identically distributed, the residuals were then plotted against the fitted values to determine if the residuals are nonrandom.

#Results

```{r exact tests, echo = FALSE}
```

17543 distinct mass to charge ratio peaks were detected in the data. Whether each peak occurred or not was tabulated for each sample, and a Fisher's Exact Test performed. This tests the null hypothesis that the occurrence of the peak is independent of the health status of the donor of the sample. After correction for multiple tests, all p-values equalled 1.

Thus, no significant effect of health on peak presence was detected.
However, so that additional analyses can be performed for the purpose of this report, uncorrected p-values were considered.
The uncorrected p-values are plotted below, with a line showing the 0.05 significance level.

```{r plot p values, echo = FALSE}
```

The number of occurences of a peak with a p-value < 0.05 was then tabulated for each sample and regressed with logistic regression, with the response variable of health status (1 for infected, and 0 for uninfected). There were 93 peaks considered. The results of the regression are shown below, including the parameter estimates and standard errors.

```{r regression 1, echo = FALSE}
```

The confidence interval of the intercept and the number of peaks is shown below.

```{r regression 2, echo = FALSE}
```

Notably, the Wald test does not indicate that either parameter is significant. This is apparent in the confidence interval, which includes 0.

The plot below shows the fit of the model to the data.

```{r regression 3, echo = FALSE}
```

The model appears to fit the data fairly well. An analysis of the residuals plotted against the predicted values (shown below) also indicates a good model fit, as there is no pattern in the residuals and they seem to vary around 0.

```{r regression 4, echo = FALSE}
```

Logistic regression does not assume residuals are normally distributed; instead, it assumes each residual is binomially distributed, with the p parameter changing over the domain of the model. However, the normal quantile-quantile plot can still be informative in detecting aberrations in the model. Thus, it is plotted below.

```{r regression 5, echo = FALSE}
```

#Discussion

This analysis concludes that peaks in mass spectrometry data cannot be used to distinguish between healthy donors and those infected with valley fever. However, this analysis was done with only 10 samples of each type of donor, and over 17,000 tests had to be performed. A larger sample size would greatly improve the power of this analysis, and may produce significant findings.

#Appendix

```{r exact tests, echo = TRUE, eval = FALSE}
```
```{r plot p values, echo = TRUE, eval = FALSE}
```
```{r regression 1, echo = TRUE, eval = FALSE}
```
```{r regression 2, echo = TRUE, eval = FALSE}
```
```{r regression 3, echo = TRUE, eval = FALSE}
```
```{r regression 4, echo = TRUE, eval = FALSE}
```
```{r regression 5, echo = TRUE, eval = FALSE}
```
