---
title: "Lab 1"
author: "Adam Orr"
date: "August 31, 2017"
output:
  pdf_document: default
  html_document: default
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(results = "hold", fig.show = "hold")
knitr::read_chunk('lab1.R')
```

## Question 1
###Script
```{r question 1, eval = FALSE}
```

###Output
```{r question 1, echo = FALSE}
```

###Answers
####Do red deer appear to have an equal sex ratio at birth?
The ratio appears to be equal to .5, but to check we should do a binomial test.
```{r Q1_question}
binom.test(sum(females),sum(c(females,males)))
```
With a p-value of 1, we cannot reject the null hypothesis that the true sex ratio is .5

## Question 2
###Script
```{r question 2, eval = FALSE}
```
###Output
```{r question 2, echo = FALSE}
```

###Answers
####Does BMI appear to depend on weight?
No, BMI does not appear to depend on weight. In this dataset, there is no clear correlation.

## Question 3
###Script
```{r question 3, eval = FALSE}
```
###Output
```{r question 3, echo = FALSE}
```

###Answers
####How do the two plots compare?
The first plot shows a curve, which appears to be a logarithmic decrease in concentration over time. 
The second plot shows that the decrease is linear after a log transform.

## Question 4
###Script
```{r question 4, eval = FALSE}
```
###Output
```{r question 4, echo = FALSE}
```

###Answers
####Does one sex seem bigger?
Females seem larger than males. To test this we can use a t-test.
```{r Q4_question}
t.test(femaleweight,maleweight, alternative="greater")
```
The T-test supports the assertion that females are bigger than males.


## Question 5
###Script
```{r question 5, eval = FALSE}
```
###Output
```{r question 5, echo = FALSE}
```

###Answers
####Based on these plots, what can you say about the usefulness of nose pigmentation for estimating lion age?
Nose pigmentation is a good estimator of lion age for male lions, but not for female lions.


