---
title: "Lab 2"
author: "Adam Orr"
date: "September 7, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
section: 91973 Friday 9am
code: lab2.R
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(results = "hold", fig.show = "hold")
knitr::read_chunk(rmarkdown::metadata$code)
```

Section: `r rmarkdown::metadata$section`

## Question 1
###Script
```{r question 1, eval = FALSE}
```

###Output
```{r question 1, echo = FALSE}
```

###Answers
####What are five of the possible combinations with three females and six males? Pick any five you please.
 * FFFMMMMMM
 * MFFFMMMMM
 * MMFFFMMMM
 * MMMFFFMMM
 * FMFMFMMMM

## Question 2
###Script
```{r question 2, eval = FALSE}
```
###Output
```{r question 2, echo = FALSE}
```

###Answers


## Question 3
###Script
```{r question 3, eval = FALSE}
```
###Output
```{r question 3, echo = FALSE}
```

###Answers
####What happens to the mean and variance of the distribution as the probability changes?
As the probability increases, the mean increases as well. On the other hand, the variance until `p = .5`, then decreases again.

####At what value is the variance of the distribution highest? Lowest?
The variance of the distribution is highest when `p = .5`. The variance is lowest when `p = .1` or `p = .9`.

## Question 4
###Script
```{r question 4, eval = FALSE}
```
###Output
```{r question 4, echo = FALSE}
```

###Answers
####What is the relationship between each bar of the cumulative plot and the bars of the distribution plot?
Each bar of the cumulative plot is the height of that bar in the distribution plot added to each bar before that one in the distribution plot.


## Question 5
###Script
```{r question 5, eval = FALSE}
```
###Output
```{r question 5, echo = FALSE}
```

###Answers

## Question 6
###Script
```{r question 6, eval = FALSE}
```
###Output
```{r question 6, echo = FALSE}
```

###Answers

## Question 7
###Script
```{r question 7, eval = FALSE}
```
###Output
```{r question 7, echo = FALSE}
```

###Answers
####Compare the average you calculated here with the mean you calculated in question 3. Do you expect them to be the same? Why or why not?
The average I calculated is `r mean(vals)`, which is very close to the average I calculated in question 3, `r p * total`. I do not expect these values to be the same due to the stochastic nature of the experiments.


