---
title: "Lab 2"
author: "Adam Orr"
date: "September 7, 2017"
code: "lab2.R"
output:
  pdf_document: default
  html_document: default
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(results = "hold", fig.show = "hold")
knitr::read_chunk(rmarkdown::metadata$code)
```

## Question 1
###Script
```{r question 1, eval = FALSE}
```

###Output
```{r question 1, echo = FALSE}
```

###Answers
####What are five of the possible combinations with three females and six males? Pick any five you please.

```{r Q1_question}
females <- c(rep(TRUE, 3),rep(FALSE, 6))
replicate(5,sample(females,9),simplify = FALSE)
```

## Question 2
###Script
```{r question 2, eval = FALSE}
```
###Output
```{r question 2, echo = FALSE}
```

###Answers


## Question 3
###Script
```{r question 3, eval = FALSE}
```
###Output
```{r question 3, echo = FALSE}
```

###Answers
####What happens to the mean and variance of the distribution as the probability changes?

####At what value is the variance of the distribution highest? Lowest?


## Question 4
###Script
```{r question 4, eval = FALSE}
```
###Output
```{r question 4, echo = FALSE}
```

###Answers
####What is the relationship between each bar of the cumulative plot and the bars of the distribution plot?
Each bar of the cumulative plot is the height of that bar in the distribution plot added to each bar before that one in the distribution plot.


## Question 5
###Script
```{r question 5, eval = FALSE}
```
###Output
```{r question 5, echo = FALSE}
```

###Answers

## Question 6
###Script
```{r question 5, eval = FALSE}
```
###Output
```{r question 5, echo = FALSE}
```

###Answers

## Question 7
###Script
```{r question 5, eval = FALSE}
```
###Output
```{r question 5, echo = FALSE}
```

###Answers

